### 2023-09-13 paper/sec-dis-pseudodata.tex
sec 2

\paragraph{SND@LHC.}
%
In the same manner as FASER, the SND@LHC experiment~\cite{SNDLHC:2022ihg}
is located in a service tunnel (TI18)
around 500 metres from the ATLAS interaction point and has been taking data
since the  beginning of Run III.
%
SND@LHC is installed off the LOS axis in order to cover the neutrino
pseudo-rapidity range of $7.2 \le \eta_\nu \le 8.4$.
%
With a total fiducial volume corresponding to a 830 kg detector with a length of 35 cm, it is composed by tungsten plates,
where neutrino scattering takes place, interleaved with nuclear emulsions and electronic tracker
components.
%
Downstream, the scattering volume is followed by a hadronic calorimeter and a muon tracking system.
%
The electromagnetic
 and hadronic energy deposits can be measured at the electronic detectors, with the emulsion
 components providing vertex reconstruction.
 %
 The lack of magnetic field prevents the charge-sign identification of the outgoing charged leptons.

@@

 \paragraph{FLArE.}
 %
 Building upon recent progress in liquid noble gas neutrino detectors over the last decade (ICARUS, MicroBooNE, SBND, DUNE), this experiment
 would rely on a modularized liquid argon (LAr) time projection detector.
 %
 The use of LAr as a target is beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimetre spatial resolution in all dimensions.
 %
 The detector will be equipped with a magnetized hadron/muon calorimeter downstream of the liquid argon volume
 for muon charge and momentum measurements.
 %
 While muon neutrinos with energy $E_\nu \gsim 2$ GeV would not be fully
 contained in the  FLArE detector,
for our projections
we assume that outgoing high-energy
muons would be measured in the FASER2 spectrometer
  situated downstream in the FPF cavern.

@@

The incoming neutrino fluxes of Ref.~\cite{Kling:2021gos} account for the geometry
and neutrino pseudo-rapidity $\eta_\nu$ coverage of the considered detector and
are encoded in Eq.~(\ref{eq:event_yields_calculation}) as $dN_{\nu}(E_\nu)/dE_{\nu}$.
%
This neutrino flux takes into account both the prompt component associated with neutrinos from charmed hadron decay as well as a displaced component from light hadron decays.
%
The prompt component used in this work was simulated at NLO using {\sc\small POWHEG}~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd} matched to {\sc\small Pythia8}~\cite{Sjostrand:2014zea, Bierlich:2022pfr} for the parton shower and hadronisation, and the displaced component was simulated with {\sc\small EPOS-LHC}~\cite{Pierog:2013ria}.
%
In comparison with Ref.~\cite{Kling:2021gos}, in addition to the updated charmed hadron production~\cite{Sominka:2023},
the neutrino flux has been updated to $\sqrt{s} = 13.6~{\rm TeV}$.

@@

>>>>

\paragraph{SND@LHC.}
%
In the same manner as FASER, the SND@LHC experiment~\cite{SNDLHC:2022ihg}
is located in a service tunnel (TI18)
around 500 meters from the ATLAS interaction point and has been taking data
since the  beginning of Run III.
%
SND@LHC is installed off the LOS axis in order to cover the neutrino
pseudo-rapidity range of $7.2 \le \eta_\nu \le 8.4$.
%
With a total fiducial volume corresponding to a 830 kg detector with a length of 35 cm, it is composed by tungsten plates,
where neutrino scattering takes place, interleaved with nuclear emulsions and electronic tracker
components.
%
Downstream, the scattering volume is followed by a hadronic calorimeter and a muon tracking system.
%
The electromagnetic
 and hadronic energy deposits can be measured at the electronic detectors, with the emulsion
 components providing vertex reconstruction.
 %
 The lack of magnetic field prevents the charge-sign identification of the outgoing charged leptons.

@@

 \paragraph{FLArE.}
 %
 Building upon recent progress in liquid noble gas neutrino detectors over the last decade (ICARUS, MicroBooNE, SBND, DUNE), this experiment
 would rely on a modularized liquid argon (LAr) time projection detector.
 %
 The use of LAr as a target is beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimeter spatial resolution in all dimensions.
 %
 The detector will be equipped with a magnetized hadron/muon calorimeter downstream of the liquid argon volume
 for muon charge and momentum measurements.
 %
 While muon neutrinos with energy $E_\nu \gsim 2$ GeV would not be fully
 contained in the  FLArE detector,
for our projections
we assume that outgoing high-energy
muons would be measured in the FASER2 spectrometer
  situated downstream in the FPF cavern.

@@

The incoming neutrino fluxes of~\cite{Kling:2021gos} account for the geometry
and neutrino pseudo-rapidity $\eta_\nu$ coverage of the considered detector and
are encoded in Eq.~(\ref{eq:event_yields_calculation}) as $dN_{\nu}(E_\nu)/dE_{\nu}$.
%
This neutrino flux takes into account both the prompt component associated with neutrinos from charmed hadron decay as well as a displaced component from light hadron decays.
%
The prompt component used in this work was simulated at NLO using {\sc\small POWHEG}~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd} matched to {\sc\small Pythia8}~\cite{Sjostrand:2014zea, Bierlich:2022pfr} for the parton shower and hadronisation, and the displaced component was simulated with {\sc\small EPOS-LHC}~\cite{Pierog:2013ria}.
%
In comparison with the calculation from~\cite{Kling:2021gos}, in addition to the updated charmed hadron production~\cite{Sominka:2023},
the neutrino flux has been updated to $\sqrt{s} = 13.6~{\rm TeV}$.

@@

The inclusive yields listed in Table~\ref{tab:integrated_rates}
differ from the total number of neutrinos interacting within the
detector volume~\cite{Feng:2022inv,Kling:2021gos} due to both the
DIS requirements  ($W^2 > 4\,{\rm GeV}^2$ and $Q^2 > 2\,{\rm GeV}^2$)
and the detector fiducial acceptances summarised in Table~\ref{tab:FPF_experiments}.
%
The former is found to be negligible, with DIS cuts removing
only  $\lesssim 1\%$ of the events, a consequence of the high energy of
LHC neutrinos.
%
The latter is quantified in Table~\ref{tab:acceptance}, displaying
the number of electron and muon neutrinos before and after applying
acceptance cuts.
%
The acceptance efficiency, defined as the ratio between pre- and post-acceptance
integrated event yields, depends on the detector and can be up to 50\%.
%
For instance, FASER$\nu$2 loses 63\% and 52\% of the interacting electron and muon
neutrinos respectively due to the acceptance requirements.
%
From Table~\ref{tab:FPF_experiments}, is it also worth noting how FLArE has virtually
perfect acceptance for electron neutrinos.
%
One also observes that SND@LHC and AdvSND exhibit relatively
large acceptance efficiencies, which however are not sufficient to compensate
the lower number of initial interacting neutrinos due to their off-axis location
as compared to FASER$\nu$(2) and FLArE.

### 2023-09-13 paper/tables/acceptance.tex
felix comments, event yields
sec 2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.70}
  \begin{tabularx}{0.8\textwidth}{p{0.3\textwidth}|c|c|c}
    \toprule
    Detector & Before Cuts & DIS Cut & Acceptance Cut \\
    \midrule
    \midrule
    FASER$\nu$ & 1.2k , 4.1k & 1.2k , 4.1k & 0.61k , 1.8k \\
    SND@LHC & 0.28k , 0.86k & 0.28k , 0.86k & 0.25k , 0.70k \\
    \midrule
    \midrule
    FASER$\nu$2 & 270k , 980k & 270k , 980k  & 172k , 510k \\
    AdvSND-far & 19k , 66k & 19k , 66k & 17k , 56k\\
    FLArE10 & 65k , 202k & 65k , 202k  & 64k , 114k \\
    FLArE100 & 427k , 1.3M &427k , 1.3M  & 420k , 680k \\
    \bottomrule
  \end{tabularx}
  \vspace{0.2cm}
\caption{Cut table showing the impact on the event yield after employing DIS cuts, $W^2 > 4{\rm GeV}^2$ and $Q^2 > 2{\rm GeV}^2$, and experimental acceptances from Table~\ref{tab:FPF_experiments}. The first number for each entry is the numer of $\nu_e + \bar{\nu}_e$ events and the second is for $\nu_{\mu} + \bar{\nu}_{\mu}$.  For the region of parameter space that we study, DIS cuts remove very few events ($\lesssim 1\%$), while acceptance cuts depend on the detector but can remove as many as 50$\%$.}
\label{tab:acceptance}
\end{table}
%-----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.70}
  \begin{tabularx}{0.99\textwidth}{p{0.26\textwidth}|c|c|c}
    \toprule
    \multirow{2}{*}{Detector} & before cuts & after DIS and acceptance cuts  & acceptance efficiency \\
    & $N_{\nu_e} + N_{\bar{\nu}_e},~N_{\nu_\mu} + N_{\bar{\nu}_\mu}$ &  $N_{\nu_e} + N_{\bar{\nu}_e},~N_{\nu_\mu} + N_{\bar{\nu}_\mu}$ &
    $N_{\nu_e} + N_{\bar{\nu}_e},~N_{\nu_\mu} + N_{\bar{\nu}_\mu}$\\
    \midrule
    \midrule
    FASER$\nu$ & 1.2k, 4.1k  & 610, 1.8k  & 51\%, 44\% \\
    SND@LHC & 280, 860 & 260, 700 & 92\%, 81\% \\
    \midrule
    \midrule
    FASER$\nu$2 & 270k, 980k   & 170k, 510k  & 63\%, 52\%\\
    AdvSND-far & 19k, 66k &  18k, 56k & 95\%, 85\%\\
    FLArE10 & 65k, 202k  & 64k, 110k & 98\%, 55\%\\
    FLArE100 & 427k, 1.3M   & 420k, 670k &98\%, 52\%  \\
    \bottomrule
  \end{tabularx}
  \vspace{0.2cm}
  \caption{The number of electron and muon neutrinos interacting within the detector volume,
    compared with the results after applying the DIS requirements  ($W^2 > 4\,{\rm GeV}^2$ and $Q^2 > 2\,{\rm GeV}^2$)
    and the experimental acceptances from Table~\ref{tab:FPF_experiments}.
    %
    The DIS requirement removes only  $\lesssim 1\%$ of the events, a consequence of the high energy of
    LHC neutrinos.
    %
    The last column displays the acceptance efficiency, defined as the ratio between pre- and post-acceptance
    integrated event yields.
    %
    While the specific efficiencies depend on the experiment, up to 50\% of the neutrinos
  interacting in the detector volume may fall outside detector acceptance. }
\label{tab:acceptance}
\end{table}
%-----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
